\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-10 paper/main.tex
.

>>>>

We developed \name{} as a method for predicting DTIs. We use an
ontology-based machine learning method \cite{} to encode phenotypic
consequences of DTIs and deep learning methods to encode molecular
features. We combine both using a protein interaction network which we
exploit using a graph neural network. We use this model to test
whether molecular or phenotype features benefit from the network
information and find that only phenotype features localize on the
graph whereas molecular features do not. We further evaluate and
compare \name{} against several DTI prediction methods and
demonstrate a substantial improvement of \name{} over the state of the
art in predicting drugs that target a protein. We also identify and
characterize several biases in both training and evaluating DTI
prediction methods, and make recommendations on how to avoid
them. \name is available as Free Software at \url{}\todo{add}.
